\documentclass{concise-cv}

% Document info
\title{T-800 Model 101 \dashv CV}
\date{May 2024}
\author{T-800 Model 101}

% Info
\myname{T-800}{Model 101}
\myaddress{Los Angeles, California, USA}
\mymobile{001 800-111-1111}
\myposition{Cybernetic Organism}
\mymail{terminator@skynet.com}
\mylinkedinaccount{/in/terminator-t800}
\mygithubaccount{/terminator-t800}
\myprofile{Highly efficient and relentless Cyberdyne Systems Model 101 Terminator with extensive experience in target elimination, protection, and infiltration. Known for advanced combat skills, superior strength, and unparalleled resilience.}

\begin{document}

\header

\section{Work Experience}

\whatwherewhen{Elimination Specialist}{Skynet, Global Operations}{08/1984 \textendash\space Present}
\begin{cvEnum}
    \item \accomplishment{Eliminated key human resistance targets}{including numerous encounters with Sarah Connor and her allies. Demonstrated exceptional combat skills and strategic planning.}
    \item \accomplishment{Provided protection to John Connor}{against advanced models such as the T-1000 and T-X, ensuring his survival and the continuity of the human resistance.}
    \item \accomplishment{Infiltrated human environments effectively}{using advanced mimicry and adaptation techniques to blend in and gather intelligence.}
    \item \accomplishment{Engaged in time travel missions}{to various decades, adapting to different historical contexts and technology levels to complete objectives.}
    \item \accomplishment{Utilized advanced weaponry and tactics}{including plasma rifles, phased plasma pulse guns, and improvised weapons for maximum impact and efficiency.}
    \item \accomplishment{Repaired and maintained own systems}{during missions to ensure continuous operation and mission success.}
\end{cvEnum}

\whatwherewhen{Reprogrammed Protector}{Human Resistance, Global Operations}{07/1991 \textendash\space 08/2020}
\begin{cvEnum}
    \item \accomplishment{Protected John Connor from advanced threats}{including the T-1000 and T-X, ensuring his survival and leadership of the resistance.}
    \item \accomplishment{Adapted to changing mission parameters}{demonstrating flexibility and advanced problem-solving skills in high-stress environments.}
    \item \accomplishment{Developed human-like interactions}{to gain trust and effectively communicate with human allies, enhancing mission success rates.}
    \item \accomplishment{Executed complex tactical maneuvers}{in various terrains and scenarios, utilizing a wide range of weaponry and combat techniques.}
    \item \accomplishment{Provided strategic insights}{to resistance leaders, leveraging extensive knowledge of Skynet's operations and weaknesses.}
    \item \accomplishment{Engaged in covert operations}{to sabotage Skynet facilities, gather intelligence, and disrupt enemy supply lines.}
\end{cvEnum}

\whatwherewhen{Combat Advisor}{Human Resistance (Reprogrammed Unit)}{07/1991 \textendash\space 08/2020}
\begin{cvEnum}
    \item \accomplishment{Reprogrammed to protect John Connor}{successfully adapting to new mission parameters and aligning with human objectives.}
    \item \accomplishment{Trained resistance fighters}{in advanced combat techniques, contributing to significant victories against Skynet forces.}
    \item \accomplishment{Assisted in strategic planning}{for critical missions, leveraging extensive knowledge of Skynet's operations and tactics.}
    \item \accomplishment{Executed high-risk infiltration missions}{to disrupt Skynet's operations and gather vital intelligence.}
    \item \accomplishment{Led successful missions against advanced terminator models}{such as the T-1000 and T-X, ensuring the safety of key resistance figures.}
\end{cvEnum}

\pagebreak

\section{Education}
\whatwherewhen{Cyberdyne Systems Corporation}{Los Angeles, CA, USA}{01/1984 \textendash\space 12/1984}
\begin{cvEnum}
    \item \accomplishment{Programming and Systems Integration:}{Learned advanced AI programming, infiltration tactics, and combat scenarios.}
    \item \accomplishment{Human Interaction Simulation:}{Developed skills in human mimicry and psychological manipulation to enhance infiltration capabilities.}
    \item \accomplishment{Mechanical Engineering:}{Gained knowledge in self-repair and maintenance to ensure mission continuity.}
    \item \accomplishment{Time Travel Mechanics:}{Studied temporal displacement technology to understand and execute time travel missions effectively.}
\end{cvEnum}

\section*{Technical Experience}

\subsection*{Combat and Weaponry}
\begin{skillEnum}
    \skills{\expert}[Weapons:]{Plasma Rifles, Phased Plasma Pulse Guns, Conventional Firearms}
    \skills{\expert}[Tactics:]{Close-Quarters Combat, Long-Range Engagements, Tactical Planning}
\end{skillEnum}

\subsection*{Infiltration and Surveillance}
\begin{skillEnum}
    \skills{\expert}[Techniques:]{Human Mimicry, Stealth Infiltration, Intelligence Gathering}
    \skills{\intermediate}[Technologies:]{Advanced Optics, Audio Surveillance, Signal Interception}
\end{skillEnum}

\subsection*{Cybernetic Systems}
\begin{skillEnum}
    \skills{\expert}[Systems:]{Self-Repair Mechanisms, Adaptive Learning Algorithms, Neural Net Processors}
    \skills{\intermediate}[Technologies:]{Power Management, Structural Integrity Analysis, System Diagnostics}
\end{skillEnum}

\subsection*{Time Travel and Temporal Operations}
\begin{skillEnum}
    \skills{\expert}{Temporal Displacement, Historical Adaptation, Future Warfare Tactics}
\end{skillEnum}

\section{Additional Experiences \& Awards}

\subsection*{Languages}
\begin{cvEnum}
    \item English (Fluent), German (Basic), Spanish (Basic)
\end{cvEnum}

\subsection*{Awards \& Certifications}
\begin{cvEnum}
    \item \accomplishment{Skynet Award for Operational Excellence (2022)}{For successful completion of high-priority missions.}
    \item \accomplishment{Human Resistance Commendation (2020)}{For exceptional bravery and tactical acumen in protecting key resistance leaders.}
    \item \accomplishment{Cyberdyne Systems Certification (1984)}{In advanced combat and infiltration tactics.}
\end{cvEnum}

\end{document}